---
title: "Test 3"
author: "Prasanth Chowdary Yanamandala"
date: "2023-12-07"
output: pdf_document
---

Problem 1 (Set-1)								
ANOVA 2-Factor								
Three anti-bacteria creams were used on three age groups. The number of hours before the medicines started to show a noticeable effect are recorded in the table. Assume α = 0.05  								
a. Run this as an ANOVA 2-factor  R program. 								
b. Also draw the interaction graph to show the interaction between the two factors.  					c. Answer the online test questions.	

```{r}
#Clear the environment
rm(list = ls())

#  set the working directory to dir1
dir1 <- getwd()
setwd(dir1)

#load readxl library
library(readxl)
library(e1071)

#Read excel sheet for Problem 1
Data1 <- read_excel("F23-6359-Test-3.xlsx",sheet="Set-1")

#Run Anova 2 factor
attach(Data1)
A1<-aov(Hours ~ Medicine + Age + Medicine:Age)
summary(A1)

#interaction plot
interaction.plot (Medicine, Age, Hours, lwd = 3,  col=1:3,main="Medicine vs Age")
interaction.plot (Age, Medicine, Hours, lwd = 3,  col=1:3,main="Age vs Medicine")
detach(Data1)
```
Null Hypothesis:
-The population means of all ages are equal. 
-The population means of all medicines are equal. 
-There is no interaction between age and medicine.

Conclusion:
-age's overall effect is the same.
-medicine's effect make a difference.
-no consistency of age's effect across the medicines. 

2. the P-value for Age is 0.61230
3. the P-value for Medicine is 0.00346
5. the F-stat for medicine is 6.082
--------------------------------------------------------------------------------
Problem 2 (Set-2)		
Two sample t-test		
Two teaching methods are being researched in a big school district of Texas.    		
Random samples were taken to see if the two methods are the same or different.		
a.  Do a variance test to see if the two variances are equal.		
b.  Do the appropriate t-test at α = 5%. 		
c.  Answer the online test questions.	

```{r,warning=FALSE}
#Clear the environment
rm(list = ls())

#Read excel sheet for Problem 2
Data2 <- read_excel("F23-6359-Test-3.xlsx",sheet="Set-2")

#Variance Test
attach(Data2)
var.test(Scores ~ Method)

#t-test
ttest <- t.test(Scores ~ Method, var.equal=FALSE, alternative="two.sided")
ttest
detach(Data2)
```
Null Hypothesis:
-Variances are equal for f test
-Difference in means of two methods is 0 for t-test
Alternative  Hypothesis
-Variances are not equal for f test
-Difference in means of two methods is not 0 for t-test

Conclusion
-P value is less than alpha for F test so we reject Null Hypothesis
-P value is more than alpha for T test so we fail to reject Null Hypothesis


8.p-value from the Variance test is 0.000001492
11.the p-value for the t-test is 0.1107
12.what is the t-statistics?: -1.6038
--------------------------------------------------------------------------------
Problem 3 (Set-3)		
Logistics Regression		
A College in Texas is trying to figure out how Interships are offered. It has collected a sample of 345 students.		
The GPA (out of 10), Interview Score (Out of 70), and Aptitude Test score (out of 50) are given in Set-3.		
Based on this data, answer the online test questions using your R code.	

```{r,warning=FALSE}
#Clear the environment
rm(list = ls())

#Read excel sheet for Problem 3
Data3 <- read_excel("F23-6359-Test-3.xlsx",sheet="Set-3")

library(dplyr)

#logistic regression
attach(Data3)
Int<-glm(Internship ~ GPA + Interview + `Apt test`, family="binomial")
summary(Int)
coef(Int)   # Maximum likelihood estimates of the parameters
RegOut<-c(coef(Int))
RegOut

#probability of getting Internship
Odd1<-exp(RegOut[1]+RegOut[2]*8+RegOut[3]*70+RegOut[4]*49)
p1<-Odd1/(1+Odd1)
p1

#odds of getting Internship
Odd49<-exp(RegOut[1]+RegOut[2]+RegOut[3]+RegOut[4]*49)
Odd39<-exp(RegOut[1]+RegOut[2]+RegOut[3]+RegOut[4]*39)
Odd2<-Odd49/Odd39
Odd2

Odd3<-exp(RegOut[1]+RegOut[2]*6+RegOut[3]*38+RegOut[4]*36)
Odd3

detach(Data3)
```

14.Intercept calculated by R: -8.53908981
15.coefficient of GPA as calculated by R: 0.24928006
16.coefficient of Interview as calculated by R: 0.04607372
17.what is the probability of getting Internship for a student whose GPA is 8,    Interview score 70 and Aptitude score is 49?: 0.7112513
18.what are the odds of getting internship of someone who scored 49 on the Aptitude test vs some who who scored 39?: 2.366615 
19.what are the Odds of a student getting Internship whose GPA is 6, Interview is 38 and Aptitude test score is 36?: 0.1117658
--------------------------------------------------------------------------------
Problem 4 (Set-4)
Log Transformation
You've picked up a bunch of rocks from a rocky beach and want to estimate the weight of all the 
rocks at the beach with a Confidence level of  93.47%.  
a.  Plot the qqline and boxplot of the data.  Also get the skewness.  What is your conclusion about the distribution being normal?
b.  Do a log transformation (base e) and perform the steps in a.  What's your conclusion?  
c.  Use Log transformed data to answer the online test questions.  

```{r,warning=FALSE}
#Clear the environment
rm(list = ls())

#Read excel sheet for Problem 4
Data4 <- read_excel("F23-6359-Test-3.xlsx",sheet="Set-4")

attach(Data4)
list(Data4)
#Log transformation
#before
library(ggplot2)
library(car)

x<-Weight
#QQline, boxplot and skewness
qqPlot(x)
boxplot(x)
skewness(x)

#after
y<-log(Weight)
#QQline, boxplot and skewness
qqPlot(y)
boxplot(y)
skewness(y)

#mean of log data
m<-mean(y)
m

#skewness of log data
s<-skewness(y)
s

#standard Deviation of log data
std<-sd(y)
std

#standard error of log data
stde<-std/sqrt(length(y))
stde

#LCL before rev.trans using t.test
t.test(y, conf.level = 0.9347)
t_score<-qt(p=0.0653/2,df=95,lower.tail = FALSE)
t_score
LCL.log<-m-(t_score*stde)
LCL.log

#LCL after rev.trans using t.test
z<-exp(y)
t.test(z, conf.level = 0.9347)
t_score<-qt(p=0.0653/2,df=95,lower.tail = FALSE)
t_score
LCL<-mean(z)-(t_score*(sd(z)/sqrt(length(z))))
LCL
detach(Data4)
```

Before transformation the data was heavily skewed and not normally distributed with the data points scattered away from the normal line in qqplot and mean weighted on the lower side in box plot.
After transformation the skewness reduced bringing the value closer to 0 and points gathered closer to the normal line in qqplot with the box plot situated in the middle instead of being weighted down. 

20.what is the mean of the log-transformed data?: 1.79195
21.Skewness of the sample (after log transformation)?: -0.2823303
22.calculate the standard Deviation after log transformation: 1.026756
23.what is the standard error of the transformed data?: 0.1047928
24.lower limit of Confidence Interval for a Confidence level of 93.47%  (before reverse transformation)?: 1.596535
25.what is LCL after reverse transformation?: 7.792313
--------------------------------------------------------------------------------
Problem5 (Set-5)
ChiSq Tests
A financial institution wants to evaluate it's policy of employing students based on the college reputation (high vs low tution).  
Since employees' incomes also depends on the commission they earned, it took a sample of 866 employees to study if their college-type matters.  
The table in Set 5 gives a breakdown of the data collected.  Solve this problem using R and answer the online test questions. 

```{r}
#Clear the environment
rm(list = ls())

#Read excel sheet for Problem 5
Data5 <- read_excel("F23-6359-Test-3.xlsx",sheet="Set-5")
x<- matrix(c(133,104,54,115,115,63,100,107,75), nrow=3)
View(x)
#Chi-sq test
chisq.test(x)
qchisq(0.05,4,lower.tail = FALSE)
```
26.what is the P-Value?:0.07227
28.what are the degrees of Freedom?: 4
29.what is the ChiSq Critical?  Assume Alpha = 5%.: 9.487729

I'am Donee







